Formalizing Stack Safety as a Security Property

### 2021-07-08 submission3/main.tex
Some little things

The protections offered by such mechanisms are commonly described in terms
of concrete examples of attacks that they can prevent---corruption
of return addresses, buffer overflows, use of uninitialized variables,
etc.---leaving a more abstract characterization to the reader's intuition.
But these mechanisms can be quite intricate, and the behaviors they prevent
can vary. Perhaps one conservatively overapproximates the ideal stack safety,
while another fails to measure up. In order to say for certain,
we need a precise, generic, and formal specification for stack
safety, as a basis both for comparing the security claims of different
enforcement techniques and for validating more rigorously that these claims
are met by particular implementations.

@@

Labeled boxes indicate an assignment of the address to a
{\em domain}---a label reflecting a particular set of intended access
rights. Unless otherwise marked, sequential addresses retain the previous domain,
as hinted by their colors. Domains are descriptive; it is up to the enforcement
mechanism to ensure that the system adheres to these permissions. Such a domain
can be \(\unsealed\) (in the stack and accessible to writes), \(\sealed{\depth}\)
(in the stack and reserved for the caller at depth \(\depth\)), or \(\outside\)
(outside the stack entirely.) These are abbreviated \(U\) and \(S(\dots)\) in the
figures. Not shown are global variables and code, which would be labeled \(\outside\).
Domains are part of the {\em context} of a machine state.
(We will introduce some other parts of the context as needed.)

@@

Before introducing the model itself, we must situate it in terms of our
assumptions about machines, enforcement mechanisms, and threats.

@@

Runtime code generation would be much more challenging to support, as
it requires dynamic code annotations. Parallelism beyond the current
coroutine model would require much more substantial changes to the machine
model. So, we consider these features out of scope.

>>>>

The protections offered by such mechanisms are commonly described in terms
of concrete examples of attacks that they can prevent---corruption of return
addresses, buffer overflows, use of uninitialized variables, etc.---leaving
a more abstract characterization to the reader's intuition.  But these
mechanisms can be quite intricate, and the behaviors they aim to prevent are
subtle and varied.  It can be hard to guess, based only on informal
intuitions, whether a given mechanism actually blocks all potential
attacks---or, conversely, whether it is overly conservative and disallows
system behaviors that are actually safe.
To settle such questions with confidence,
we need a precise, generic, and formal specification for stack
safety, as a basis both for comparing the security claims of different
enforcement techniques and for validating that these claims
are met by particular implementations.

@@

Labeled boxes indicate an assignment of the address to a
{\em domain}---a label reflecting a particular set of intended access
rights. Unless otherwise marked, sequential addresses retain the previous domain,
as hinted by their colors. Domains are descriptive\bcp{??}; it is up to the enforcement
mechanism to ensure that the system adheres to these permissions. Such a domain
can be \(\unsealed\) (in the stack and accessible to writes), \(\sealed{\depth}\)
(in the stack and reserved for the caller at depth \(\depth\)), or \(\outside\)
(outside the stack entirely.) These are abbreviated \(U\) and \(S(\dots)\) in the
figures. Not shown are global variables and code, which would be labeled \(\outside\).
Domains form part of the {\em context} associated with a machine state.
(We will introduce some other parts of the context as needed.)

@@

Before introducing the model itself, let us set the context by stating some
assumptions we are making about machines, enforcement mechanisms, and
potential threats.

@@

Runtime code generation would be much more challenging to support, as
it requires dynamic code annotations. Similarly, parallelism beyond the current
coroutine model would require more substantial changes to the machine
model. We consider these features out of scope for now.
